Scalable Clustering of Genotype Information using MapReduce

### 2014-11-07 doc/publications/journal2014/paper.tex
Hardware section

\subsection*{Hardware}
We processed the data using a Portable Batch System (PBS) cluster. We allocated one node and 64GB memory for the comparison between Mahout and R.
Each node has eight CPU cores, however both applications run a single thread for pre-processing the data.
%TODO check numbers are correct ?
For the \SixReal\ and \FullReal\ dataset, we ran the job on a PBS cluster of 5 nodes, with twelve CPU cores and 48GB of memory per node.

>>>>

\subsection*{Hardware}
We processed the data using a cluster of VMs on the Microsoft Azure cloud service. Each of the VMs has 7GB memory and and 4 CPU cores.
Six of the VMs have the YARN NodeManager installed, and therefore these 6 machines process the data. The seventh machine dedicates the majority of its memory to
the HDFS NameNode, ResourceManager and monitoring services. An eighth, single core machine, hosts the Cloudera manager service.
With the 6 quad-core machines, we can run a total of 24 YARN containers simultaneously.

We used a single VM for the comparison between Mahout and R.
For the \SixReal\ and \FullReal\ dataset, we ran the job on a PBS cluster of 5 nodes, with twelve CPU cores and 48GB of memory per node.
